Results

### 2021-07-23 Analysis/03_Summarise_results.Rmd
boring results tables

```{r, echo = FALSE}
kable(null_table, caption = "Difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "alpha", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "dispersion", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "evenness", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

>>>>

```{r, echo = FALSE}
## Even fancier column names
colnames(null_table) <- gsub(".d_rm", ".rm", colnames(null_table))
colnames(null_table) <- gsub("equalizing", "equa", colnames(null_table))
colnames(null_table) <- gsub("facilitation", "faci", colnames(null_table))
colnames(null_table) <- gsub("filtering", "filt", colnames(null_table))
colnames(null_table) <- gsub("competition", "comp", colnames(null_table))
kable(null_table, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "tree_alpha", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "tree_dispersion", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "tree_evenness", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```
